\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-24 OaklandSubmission/intro.tex
sec 1.1

@@

In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
computation. We provide the first compiler where the developer writes a high-level program and the compiler automatically generates an efficient \mpc protocol that uses a
mix of arithmetic and boolean circuits. 
It is compatible with any implementation of \mpc that allows a mix of arithmetic and boolean circuits. 
We focus on semi-honest secure two-party computation and use ABY \cite{aby} as the suitable cryptographic back-end.
We provide a formal type system and operational semantics for our language and prove correctness and security of our compiler.
We evaluate our system on wide range of benchmarks for secure prediction \cite{shafindss,wu,barni,secureml,minionn,bonsai} using linear classifier, decision trees and deep neural networks, matrix factorization \cite{valeriaMatrix} and training of deep neural network \cite{secureml}. Our evaluations show that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). \TODO{Add some text to increase enthusiasm about results.} Moreover, unlike previous systems such as \cite{wysteria,aby}, our system can scale to arbitrarily large computations using {\em secure code partitioning} (see below). \divya{I think we can skip Yao pipelining here, right?}
Hence, we show that our framework achieves all four properties of programmability, generality, performance, and scalability.

Prior to our work, there have been systems that provide only a subset of the above properties and lack in remaining properties. For instance, using the framework of CBMC-GC \cite{cbmcgc}, one can write functionalities in high-level language like C but it gives poor performance due to its usage of boolean circuits as underlying representation. Similarly, ABY framework can potentially give good performance but is not programmable. Technique of pipelining Yao garbled circuits \cite{yao-pipe} allowed scaling to lage circuits but gives poor performance. \divya{what about programming?} To summarize, none of the prior frameworks could be used to evaluate the benchmarks such as linear regression, deep neural network prediction etc. In fact, it was widely believed that generic 2PC would not scale to the secure prediction and hence, various protocols were hand-crafted for this task \cite{shafindss,wu,secureml,minionn}. Our framework contradicts this belief.

In this work, we solve an interesting design problem to give a user friendly language that is expressive enough together with a compiler generating efficient secure 2PC protocols.
Programmability and performance of our system has enabled us to write large programs whose circuits  exhaust the memory of the system (~32 GB). To combat this issue, we give a technique called pipelining (see below) that allows scaling of our  scaling of our framework to arbitrary size computations.

@@

\textbf{Programmability.} \tool is a programmer-friendly framework to
express the function to be computed and uses a mix of arithmetic and
boolean \mpc back-ends. We illustrate the above toy example of $w^Tx
>b$ in our language in \figureref{ex-sml}. As is clear from the code,
the programmer is not required to write keywords such as {\em secret}
or {\em public} and can remain completely oblivious of the
cryptographic back-end. In contrast, \figureref{ex-aby} illustrates
the same example using the framework in ABY \cite{aby}. Here, as
already mentioned, the programmer needs to write the low level gates
like {\tt MULT, ADD, CONS, GT}, etc. The programmer is also required
to use the appropriate share conversion gates such as {\tt A2Y} that
converts Arithmetic shares to Yao shares. Moreover, it is easy to
maintain code in \tool and small change to the functionality requires
only a small change in the code. In contrast, working with ABY, even
for a small change a developer might have to re-work the whole circuit
for efficiency reasons. We describe these examples in detail in
\sectionref{ex}.

\textbf{Performance.} Our compiler is aware of cryptographic costs of different representations and inter-conversions.  Based on these costs, our compiler, given a program in \tool, automatically picks Arithmetic and Boolean representations for different sub-parts of the program and inserts the required inter-conversions as well. 
Our experiments show that automatically generated protocols using \tool match the performance of tailor-made protocols in \cite{minionn,shafindss} (see \sectionref{eval}). This shows that  \tool achieves generality, performance and programmer productivity. These features allow us to evaluate our system on a variety of benchmarks, especially, state-of-the-art ML prediction algorithms with \emph{real} data and models.

@@

\textbf{Pipelining.} Another issue in adoption of \mpc is difficulty in scaling to large programs. 
%In general, \mpc implementations struggle in scaling to large programssize of memory on a system limits the largest compute inside the SMC and hence,. 
The reason being all \mpc implementations use a circuit-like representation as an intermediate representation. Hence, the largest compute that can be done securely is upper-bounded by the largest circuit that can fit in memory on a machine. \nc{Should we point out here that ABY itself has an explicit limit on circuit size and also give an example of a program that easily surpasses this bound? Also, hadnt ABY also said something about this? If so, we can mention this.}
To address this issue, we develop a technique called \emph{pipelining} that allows us to run arbitrarily large programs. At a high level, we break the original program into a sequence of small sub-programs and mask the intermediate outputs using secure secret sharing between the two parties. We appropriately append the share-reconstruction function to the beginning of the subsequent sub-program. Now, we execute each of these sub-programs sequentially in our framework. We provide details of pipelining and prove the correctness and security of this transformation in \sectionref{pipe}.

>>>>

  \TODO{While taking a pass on intro, check citation correctness or if we are missing any citation.}

@@

In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
computation. We provide the first compiler where the developer writes a high-level program and the compiler automatically generates an efficient \mpc protocol that uses a
mix of arithmetic and boolean circuits. 
It is compatible with any implementation of \mpc that allows a mix of arithmetic and boolean circuits. 
We focus on semi-honest secure two-party computation and use ABY \cite{aby} as the suitable cryptographic back-end.
We provide a formal type system and operational semantics for our language and prove correctness and security of our compiler.
We evaluate our system on wide range of benchmarks for secure prediction \cite{shafindss,wu,barni,secureml,minionn,bonsai} using linear classifier, decision trees and deep neural networks, matrix factorization \cite{valeriaMatrix} and training of deep neural network \cite{secureml}. Our evaluations show that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). \TODO{Add some text to increase enthusiasm about results.} Moreover, unlike previous systems such as \cite{wysteria,aby,cbmcgc}, our system can scale to arbitrarily large computations using our technique of {\em secure code partitioning} (see below). \divya{I think we can skip Yao pipelining here, right?}
Hence, we show that our framework achieves all four properties of programmability, generality, performance, and scalability (see below for details).

Prior to our work, there have been systems that provide only a subset of the above properties. For instance, using the framework of CBMC-GC \cite{cbmcgc} allows  functionalities to be expressed in high-level language C but it gives poor performance due to its usage of boolean circuits as underlying representation. Similarly, ABY \cite{aby} framework can potentially give good performance (due to mix of boolean and arithmetic circuits) but is not programmable. Yao's garbled circuits \cite{yao} work with boolean circuits and are the most widely used 2PC protocols but they  do not scale to large functions due to large memory requirement.
Huang et al. \cite{yao-pipe} gave the technique of pipelining Yao's garbled circuits that enabled scaling to large functions but still gives poor performance due to its use of boolean circuit representation. 
To summarize, none of the prior frameworks have been used to evaluate the benchmarks such as secure prediction using linear regression, decision trees, deep neural networks, etc. In fact, it was widely believed that generic 2PC would not scale to the secure prediction and hence, various protocols were hand-crafted for this task \cite{shafindss,wu,secureml,minionn}. Our framework contradicts this belief (see below).

In this work, we solve the design problem to provide a user friendly language that is expressive and can be compiled to efficient secure 2PC protocols.
Programmability in \tool and performance of generated protocols has enabled us to write large programs whose circuits  exhaust the memory of the system (~32 GB). To combat this issue, we give a technique called secure code partitioning (see below) that allows scaling of \tool to arbitrary size computations.

@@

\textbf{Programmability.} \tool is a programmer-friendly framework to
express the function to be computed and uses a mix of arithmetic and
boolean \mpc back-ends. We illustrate the above example of $w^Tx
>b$ in our language in \figureref{ex-sml}. 
As is clear from the code, the programmer can remain completely oblivious of the cryptographic back-end and underlying circuit representation. 
Also,  the programmer is not required to write keywords such as {\em secret}
or {\em public} (that are required by languages like Wysteria \cite{wysteria}). 
 In contrast, \figureref{ex-aby} illustrates
the same example using the framework in ABY \cite{aby}. Here, as
already mentioned, the programmer needs to create shares and write the low level gates
like $\mathtt{MUL, ADD, CONS, GT}$, etc \TODO{make these fonts consistent}. The programmer is also required
to use the appropriate share conversion gates such as $\mathtt{A2Y}$ that
converts arithmetic shares to Yao-based boolean shares to be used in comparison after the inner-product computation.
Moreover, it is easy to
maintain code in \tool and a small change to the functionality requires
only a small change in the code. In contrast, working with ABY, even
for a small change a developer might have to re-work the whole circuit
for efficiency reasons. We elaborate on these examples  in
\sectionref{ex}.

\textbf{Generality and Performance.} Our compiler is aware of cryptographic costs of different representations and corresponding inter-conversions.  Based on these costs, our compiler, given a program in \tool, automatically picks arithmetic and boolean representations for different sub-parts of the program and inserts the required inter-conversions as well. 
We demonstrate the generality of our framework by writing a wide range of functionalities in \tool such as linear regression, deep neural networks, decision trees and matrix factorization.
Our evaluations show that automatically generated protocols using \tool are competitive with tailor-made protocols in \cite{shafindss,wu,barni,minionn,secureml,valeriaMatrix} (see \sectionref{eval}). These features allow us to evaluate our system state-of-the-art ML prediction algorithms, e.g., \sectionref{eval} describes evaluation on ML models from a recent ICML paper \cite{bonsai} and Tensorflow \cite{tensorflow}.

@@

\textbf{Secure Code Partitioning (or Partitioning in short).} Another issue in adoption of \mpc is difficulty in scaling to large programs. 
%In general, \mpc implementations struggle in scaling to large programssize of memory on a system limits the largest compute inside the SMC and hence,. 
The reason being most \mpc implementations use a circuit-like representation as an intermediate representation. Hence, the largest compute that can be done securely is upper-bounded by the largest circuit that can fit in memory on a machine. \nc{Should we point out here that ABY itself has an explicit limit on circuit size and also give an example of a program that easily surpasses this bound? Also, hadnt ABY also said something about this? If so, we can mention this.}
To address this issue, we develop a technique called partitioning that allows us to run arbitrarily large programs. At a high level, we break the original program into a sequence of small sub-programs and mask the intermediate outputs using a secure secret sharing between the two parties. We appropriately append the share-reconstruction function to the beginning of the subsequent sub-program. Now, we execute each of these sub-programs sequentially in our framework. We provide details of partitioning and prove the correctness and security of this transformation in \sectionref{pipe}.
